### 2021-01-21 research project/sections/Background.tex
""

Let $A_{n}$ equal the area of the polygon with $n$ sides as such: \\
$A_{n} = \frac{OH \cdot BD \cdot n}{2}$ \\
$A_{n} = \frac{R \cos{\alpha} \cdot 2 R \sin{\alpha} \cdot n}{2} = n R^2 \sin{\alpha} \cos{\alpha}$

@@

So

\begin{figure}[!h]
\definecolor{qqwuqq}{rgb}{0,0.39215686274509803,0}
\definecolor{uuuuuu}{rgb}{0.26666666666666666,0.26666666666666666,0.26666666666666666}
\definecolor{xdxdff}{rgb}{0.49019607843137253,0.49019607843137253,1}
\definecolor{qqqqzz}{rgb}{0,0,0.6}
\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=0.7]
\clip(-8.372520930232552,-8.50470697674418) rectangle (7.69259534883721,7.028316279069767);
\draw [shift={(-0.03355999206952884,0)},line width=1pt,color=qqwuqq,fill=qqwuqq,fill opacity=0.10000000149011612] (0,0) -- (0:1.3302325581395344) arc (0:44.77428433325932:1.3302325581395344) -- cycle;
\draw [line width=0.8pt,color=qqqqzz] (0,0) circle (6cm);
\draw [line width=1pt] (4.242640687119286,4.242640687119285)-- (6,0);
\draw [line width=1pt] (6,0)-- (4.242640687119286,-4.242640687119285);
\draw [line width=1pt] (4.242640687119286,-4.242640687119285)-- (4.242640687119286,4.242640687119285);
\draw [line width=1pt] (-6,0)-- (6,0);
\draw [line width=1pt] (-4.275936263984878,-4.209081736713964)-- (4.242640687119286,4.242640687119285);
\draw [line width=1pt] (-4.242640687119285,4.242640687119286)-- (4.242640687119286,-4.242640687119285);
\draw [line width=1pt] (-0.03355999206952884,0)-- (5.121320343559643,2.1213203435596424);
\draw [line width=1pt] (-4.242640687119285,4.242640687119286)-- (-4.275936263984878,-4.209081736713964);
\begin{scriptsize}
\draw [fill=xdxdff] (4.242640687119286,4.242640687119285) circle (2.5pt);
\draw[color=xdxdff] (4.4772465116279085,4.623665116279071) node {$B$};
\draw [fill=xdxdff] (-4.242640687119285,4.242640687119286) circle (2.5pt);
\draw[color=xdxdff] (-4.295311627906972,4.623665116279071) node {$A$};
\draw [fill=xdxdff] (-4.275936263984878,-4.209081736713964) circle (2.5pt);
\draw[color=xdxdff] (-4.336241860465112,-4.55) node {$C$};
\draw [fill=xdxdff] (6,0) circle (2.5pt);
\draw[color=xdxdff] (6.237246511627907,0.3873860465116302) node {$E$};
\draw [fill=xdxdff] (4.242640687119286,-4.242640687119285) circle (2.5pt);
\draw[color=xdxdff] (4.3772465116279085,-4.5) node {$D$};
\draw[color=black] (5.3595720930232575,2.3111069767441874) node {$H'$};
\draw [fill=xdxdff] (5.12,2.12) circle (2.5pt);
\draw[color=black] (3.947479069767444,-0.615404651162788) node {$H$};
\draw [fill=xdxdff] (4.242640687119286,0) circle (2.5pt);
\draw [fill=xdxdff] (0,0) circle (2.5pt);
\draw[color=uuuuuu] (0.00003720930232879,-0.3464558139534907) node {$O$};
\draw[color=qqwuqq] (1.5325953488372117,0.3873860465116302) node {$\alpha$};
\end{scriptsize}
\end{tikzpicture}
\label{fig:image1}
\caption{Circle with 1 segment from a $n$-gon with point $H$ and 2 
segments from an $2n$-gon, one of which on point $H'$, inscribed in 
a circle of radius $OB$}
\end{figure}

>>>>

Let $A_{n}$ equal the area of the polygon with $n$ sides as such: \\
$A_{n} = \frac{OH \cdot BD \cdot n}{2}$ \\
$= \frac{R \cos{\alpha} \cdot 2 R \sin{\alpha} \cdot n}{2} = n R^2 \sin{\alpha} \cos{\alpha}$

@@

So it can be written that, by definition,

$\frac{A_{n}}{A_{2n}} = \frac{n R^2 \sin{\alpha} \cos{\alpha}}{2 n R^2 \sin{\frac{\alpha}{2}} \cos{\frac{\alpha}{2}}} = \frac{\sin{2 \alpha}}{2 \sin{\alpha}}$

Which through the trigonometric identity... // todo

\begin{figure}[!h]
\definecolor{qqwuqq}{rgb}{0,0.39215686274509803,0}
\definecolor{uuuuuu}{rgb}{0.26666666666666666,0.26666666666666666,0.26666666666666666}
\definecolor{xdxdff}{rgb}{0.49019607843137253,0.49019607843137253,1}
\definecolor{qqqqzz}{rgb}{0,0,0.6}
\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=0.7]
\clip(-8.372520930232552,-8.50470697674418) rectangle (7.69259534883721,7.028316279069767);
\draw [shift={(-0.03355999206952884,0)},line width=1pt,color=qqwuqq,fill=qqwuqq,fill opacity=0.10000000149011612] (0,0) -- (0:1.3302325581395344) arc (0:44.77428433325932:1.3302325581395344) -- cycle;
\draw [line width=0.8pt,color=qqqqzz] (0,0) circle (6cm);
\draw [line width=1pt] (4.242640687119286,4.242640687119285)-- (6,0);
\draw [line width=1pt] (6,0)-- (4.242640687119286,-4.242640687119285);
\draw [line width=1pt] (4.242640687119286,-4.242640687119285)-- (4.242640687119286,4.242640687119285);
\draw [line width=1pt] (-6,0)-- (6,0);
\draw [line width=1pt] (-4.275936263984878,-4.209081736713964)-- (4.242640687119286,4.242640687119285);
\draw [line width=1pt] (-4.242640687119285,4.242640687119286)-- (4.242640687119286,-4.242640687119285);
\draw [line width=1pt] (-0.03355999206952884,0)-- (5.121320343559643,2.1213203435596424);
\draw [line width=1pt] (-4.242640687119285,4.242640687119286)-- (-4.275936263984878,-4.209081736713964);
\begin{scriptsize}
\draw [fill=xdxdff] (4.242640687119286,4.242640687119285) circle (2.5pt);
\draw[color=xdxdff] (4.4772465116279085,4.623665116279071) node {$B$};
\draw [fill=xdxdff] (-4.242640687119285,4.242640687119286) circle (2.5pt);
\draw[color=xdxdff] (-4.295311627906972,4.623665116279071) node {$A$};
\draw [fill=xdxdff] (-4.275936263984878,-4.209081736713964) circle (2.5pt);
\draw[color=xdxdff] (-4.336241860465112,-4.55) node {$C$};
\draw [fill=xdxdff] (6,0) circle (2.5pt);
\draw[color=xdxdff] (6.237246511627907,0.3873860465116302) node {$E$};
\draw [fill=xdxdff] (4.242640687119286,-4.242640687119285) circle (2.5pt);
\draw[color=xdxdff] (4.3772465116279085,-4.5) node {$D$};
\draw[color=black] (5.3595720930232575,2.3111069767441874) node {$H'$};
\draw [fill=xdxdff] (5.12,2.12) circle (2.5pt);
\draw[color=black] (3.947479069767444,-0.615404651162788) node {$H$};
\draw [fill=xdxdff] (4.242640687119286,0) circle (2.5pt);
\draw [fill=xdxdff] (0,0) circle (2.5pt);
\draw[color=uuuuuu] (0.00003720930232879,-0.3464558139534907) node {$O$};
\draw[color=qqwuqq] (1.5325953488372117,0.3873860465116302) node {$\alpha$};
\end{scriptsize}
\end{tikzpicture}
\label{fig:image1}
\caption{Circle with 1 segment from a $n$-gon with point $H$ and 2 
segments from an $2n$-gon, one of which on point $H'$, inscribed in 
a circle of radius $OB$, adapted from \cite{borisgourevitch2013}}
\end{figure}
